---
title: "introduction"
author: "Jan Korevaar"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Package Description

`fars_functions` package reads and plots Fatality Analysis Reporting System (FARS) data 
from the National Highway Traffic Safety Administration. [FARS](https://en.wikipedia.org/wiki/Fatality_Analysis_Reporting_System)


## Load Packages

```{r}
library(farsfunctions)
```


## Included data

Data files included within the package are:

```{r}
list.files(system.file("extdata", package = "farsfunctions"))
```


## Package Functionsdev

### Function `make_filename`

This function returns file name and path to the data files:

```{r}
make_filename(year = 2013)
```

### Function `fars_read_years`

Ancillary function used by `fars_summarize_years`

```{r}
fars_read_years(years = c(2013, 2014, 2015))
```

# Links:
* [Package fars GitHub](https://github.com/jkorevaar/farsdata)
